### 2020-11-03 latex/vlp.tex
Updated a typo before sending VLP proof to Manfredi.

   We conclude that the VNHC is injecting energy into the VLP.
   By flipping the inequality of (\ref{eqn:vlp-energy-gain-condition})
   we find the VLP is gaining energy in negative-time, so the VNHC would be
   dissipating energy.
\end{proof}

>>>>

   We conclude that the VNHC is injecting energy into the VLP.
   By flipping the inequality of (\ref{eqn:vlp-energy-gain-condition})
   we find the VLP is gaining energy in negative-time, so the VNHC is
   dissipating energy.
\end{proof}
